An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
try to stop code from wrapping screens
figured out full width images
Signed-off-by: andrew <andrew@textile.io>
full width code example
Signed-off-by: andrew <andrew@textile.io>
figure embed, code blocks etc
Signed-off-by: andrew <andrew@textile.io>

@@

@@

    // Sig is a cryptographic signature of Event and Refs
    // created with the Log's private key.
    Sig() []byte
}
\end{lstlisting}

\begin{lstlisting}
// Event represents the content of an update.
// Note: In practice, this is encrypted with the Read key.
type Event interface {
    ipld.Node

    // Decrypt is a helper function that decrypts Body
    // with a key in Header.
    Decrypt() (ipld.Node, error)
}
\end{lstlisting}
\begin{lstlisting}
// EventHeader contains Event metadata.
type EventHeader interface {
    ipld.Node

    // Key is an optional single-use symmetric key
    // used to encrypt Body.
    Key() []byte
}
\end{lstlisting}

@@

@@

\tiny
\textbf\textit /ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab\\
\normalsize

In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress:\\

\tiny
\textbf\textit /ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab\\
\normalsize

@@

\begin{lstlisting}
// AddrBook stores log addresses
type AddrBook interface {
   AddAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   AddAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   SetAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   SetAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   UpdateAddrs(t thread.ID, id peer.ID, oldTTL time.Duration, newTTL time.Duration)
   Addrs(thread.ID, peer.ID) []ma.Multiaddr
   ClearAddrs(thread.ID, peer.ID)
}
\end{lstlisting}

@@

Followers are represented as additional addresses, meaning that a Log address book may contain multiple multiaddresses for a single Log:

\begin{lstlisting}
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{boat.jpg}
  \caption{The three layers of Log Event encryption.}
  \label{fig:boat1}
\end{figure}

@@

\begin{lstlisting}
// KeyBook stores log keys
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}

@@

\begin{lstlisting}
type TextileKVStore interface {
  Put(key string, value interface{}) error
  Get(key string) (interface{}, error)
  Del(key string) error
}
\end{lstlisting}

@@

\begin{lstlisting}
type TextileDocumentStore interface {
  Put(doc Inedexable) error
  Get(key string) (Indexable, error)
  Del(key string) error
  Query(query Query) ([]Indexable, error)
}
\end{lstlisting}

@@

\begin{lstlisting}
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k", // TID
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
    "12D..dJT6nXY": ["follow"],
    "12D..P2c6ifo": ["read"],
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k-acl", // TID-acl
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
  }
}
\end{lstlisting}

@@

@@

@@

\bibliographystyle{compj}
% \bibliography{ModellingBidders}
\input{draft.bbl}

>>>>

% for full width figures\
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{graphicx}% http://ctan.org/pkg/graphicx

@@

% color the json
\lstdefinelanguage{json}{
  basicstyle={\small\ttfamily},
  numbers=none,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    backgroundcolor=\color{white},
    literate=
     *{0}{{{\color{black}0}}}{1}
      {1}{{{\color{black}1}}}{1}
      {2}{{{\color{black}2}}}{1}
      {3}{{{\color{black}3}}}{1}
      {4}{{{\color{black}4}}}{1}
      {5}{{{\color{black}5}}}{1}
      {6}{{{\color{black}6}}}{1}
      {7}{{{\color{black}7}}}{1}
      {8}{{{\color{black}8}}}{1}
      {9}{{{\color{black}9}}}{1}
      {:}{{{\color{gray}{:}}}}{1}
      {\{}{{{\color{gray}{\{}}}}{1}
      {\}}{{{\color{gray}{\}}}}}{1}
      {[}{{{\color{gray}{[}}}}{1}
      {"}{{{\color{gray}{"}}}}{1}
      {,}{{{\color{gray}{,}}}}{1}
      {]}{{{\color{gray}{]}}}}{1},
}

@@

TODO: Ref to appendix

@@

\begin{figure*}
\centering
\begin{minipage}{0.6\textwidth}
\begin{lstlisting}
// Log multiaddress
ipel := "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Encapsulated multiaddress
address := "/ip4/127.0.0.1/tcp/1234/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab"

// Address book
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}
\end{minipage}
  \caption{The Log Multiaddress.}
  \label{fig:boat1}
\end{figure*}

@@

TODO: ref to embed

In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress:

TODO: ref to embed

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
// AddrBook stores log addresses
type AddrBook interface {
   AddAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   AddAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   SetAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   SetAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   UpdateAddrs(t thread.ID, id peer.ID, oldTTL time.Duration, newTTL time.Duration)
   Addrs(thread.ID, peer.ID) []ma.Multiaddr
   ClearAddrs(thread.ID, peer.ID)
}
\end{lstlisting}
\end{minipage}

@@

Followers are represented as additional addresses, meaning that a Log address book may contain multiple multiaddresses for a single Log

TODO: ref to embed

@@

\begin{figure*}
\centering
\begin{minipage}{0.6\textwidth}
  \includegraphics[width=\linewidth]{figures/Event_Log_With_Encryption.png}
  \caption{The three layers of Log Event encryption.}
  \label{fig:LogEncryption}
  \end{minipage}
\end{figure*}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
// KeyBook stores log keys
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileKVStore interface {
  Put(key string, value interface{}) error
  Get(key string) (interface{}, error)
  Del(key string) error
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileDocumentStore interface {
  Put(doc Inedexable) error
  Get(key string) (Indexable, error)
  Del(key string) error
  Query(query Query) ([]Indexable, error)
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k", // TID
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
    "12D..dJT6nXY": ["follow"],
    "12D..P2c6ifo": ["read"],
  }
}
\end{lstlisting}
\end{minipage}

@@

\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k-acl", // TID-acl
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
  }
}
\end{lstlisting}

@@

\begin{figure*}
  \includegraphics[width=\textwidth,height=4cm]{boat.jpg}
  \caption{This is a full width boat.}
  \label{fig:boat1}
\end{figure*}

@@

\begin{figure*}

    // Sig is a cryptographic signature of Event and Refs
    // created with the Log's private key.
    Sig() []byte
}

// Event represents the content of an update.
// Note: In practice, this is encrypted with the Read key.
type Event interface {
    ipld.Node

    // Decrypt is a helper function that decrypts Body
    // with a key in Header.
    Decrypt() (ipld.Node, error)
}

// EventHeader contains Event metadata.
type EventHeader interface {
    ipld.Node

    // Key is an optional single-use symmetric key
    // used to encrypt Body.
    Key() []byte
}
\end{lstlisting}
  \caption{This is a full width code block.}

\end{figure*}

@@

\bibliographystyle{compj}
% \bibliography{ModellingBidders}
\input{whitepaper.bbl}
